# Power analysis examples\vspace{3pt}

## Surrogate modeling for simulation-based power analysis {.allowframebreaks}

[@zimmer_sample_2023; @zimmer_simulation-based_2023]
\vspace{\baselineskip}

Aim

- Support simulation-based power-analysis given
  - Multiple design parameters (e.g., ...)
  - Budget constraints

Scope

- Find cost-optimal solution among the ones with desired power (e.g., $\ge 0.95$)
- Find power-optimal solution among the ones with desired costs (e.g., $\le X$ EUR)


Approach 

- Monte Carlo simulations, in combination with
- Model-guided search of the design-parameter space (surrogate modeling)
- R-package [*mlpwr*](https://cran.r-project.org/web/packages/mlpwr/index.html) 


\newpage


(ref:cap-mlpwr1) Power for multiple design parameters [from @zimmer_sample_2023]

```{r mlpwr1, fig.cap = "(ref:cap-mlpwr1)", echo = FALSE, out.width="0.3\\textwidth", fig.align = 'center'}
knitr::include_graphics("media/zimmer24_fig1.pdf")
```


\newpage

:::::::::::::: {.columns .onlytextwidth}
::: {.column width="60%"}

Initialisation phase

  - Simulate power for initial sets of design parameter combinations
  
Prediction phase

  - Estimate model to approximate relationship between power and design parameters
  - Based on model-implied relationship / model predictions, find (conditionally) optimal design parameter combination
  
Updating phase

  - Simulate power for conditionally optimal design parameter combination
  
Termination

  - Different criteria (e.g., desired model accuracy)

:::
::: {.column width="40%"}

(ref:cap-mlpwr2) Surrogate modeling algorithm [from @zimmer_sample_2023]

```{r mlpwr2, fig.cap = "(ref:cap-mlpwr2)", echo = FALSE, out.width="0.9\\textwidth", fig.align = 'right'}
knitr::include_graphics("media/zimmer24_fig9.pdf")
```
:::
::::::::::::::

\newpage

Surrogate model for single design parameter

  - Logistic regression 
  
Surrogate model for multiple design parameters

  - Gaussian process regression
  - Support vector regression



\newpage

Demo t-test

```{r mlpwr3, echo = TRUE}
simfun <- function (N) {
  # Generate a data set
  dat <- rnorm(n = N, mean = 0.3 , sd = 1)
  # Test the hypothesis
  res <- t.test(dat)
  res$p.value < 0.01
}
```


\newpage

Demo t-test

```{r mlpwr4, echo = TRUE}
res <- mlpwr::find.design(
  simfun = simfun, 
  boundaries = c(100, 300), 
  power = 0.95
  )
# additional arguments, e.g.
# costfun
# cost
# surrogate
# n.startsets

```

\newpage

Demo t-test

```{r mlpwr5, echo = TRUE}
summary(res)

```

\newpage

Demo t-test

```{r mlpwr6,echo = TRUE, out.width="0.7\\textwidth", fig.align = 'center'}
plot(res)

```


\newpage

Demo mixed model

(ref:cap-mlpwr7) Result for multiple design dimensions [from @zimmer_sample_2023]

```{r mlpwr7, fig.cap = "(ref:cap-mlpwr7)", echo = FALSE, out.width="0.4\\textwidth", fig.align = 'center'}
knitr::include_graphics("media/zimmer24_fig5.pdf")
```

